---
title: "European Car Engines"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: lumen
    css: "sidebar.css"
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
source("Git_0000_src_cd_librariesPCA.R")
source("Git_0010_src_cd_PCA_CarNrg.R")
source("Git_0011_src_cd_CarNrg_TS.R")
source("Git_0012_src_cd_CarNrg_Map.R")

```


Registration Maps {data-orientation=rows}
===============================================================================

```{r reactives_reg_maps}

### Preparing map data
react_car_Maps <- reactive({

  if (input$car_Variable == "Cluster ID"){
    
    data_Maps <- PCA_CAR_NRG_imp_glong %>% 
      filter(Year == input$car_Year) %>% 
    select(Country, ClusterID)  } else {
      
       if (input$car_Variable == "GDP per Capita") {
         
         data_Maps <- PCA_CAR_NRG_imp_glong %>% 
      filter(Year == input$car_Year) %>% 
    select(Country, GDP_cap) } else {
      
    data_Maps <- PCA_CAR_NRG_imp_glong %>% 
      filter(Year == input$car_Year) %>% 
    select(Country, Energy, Registration) %>% 
      filter(Energy == input$car_Variable)
      
    }
      
      
    }

    data_Maps
    
    
  })


### Plotting Map data

react_car_leaf <- reactive({
  
  data_leaf = react_car_Maps()
  
  if (input$car_Variable == "Cluster ID"){

    
     factpal <- colorFactor(palette = "Dark2", 
                       data_leaf$ClusterID,
                       n = 5)
      

     leaf_Maps = leaflet(data = data_leaf, 
          #                %>% 
          # filter(Year == input$car_Year),
        options = leafletOptions(minZoom = 2, maxZoom = 5)) %>% 
  setView(lng = 15, lat = 55, zoom = 3) %>% 
  addProviderTiles(providers$CartoDB.Positron,
                   options = providerTileOptions(opacity = 0.5)) %>% 
  addPolygons(stroke = FALSE,
    # color = "grey", 
    #           opacity = .5,
    #           stroke = TRUE, 
              smoothFactor = 0.2, 
              fillOpacity = .7,
              color = ~factpal(data_leaf$ClusterID),
              label = ~paste0("Country: ", 
                              Country , 
                              " - ",
                              "Cluster ID: ", 
                              ClusterID),
              highlight = highlightOptions(weight = 2,
                                           color = "white",
                                           bringToFront = TRUE)) %>% 
  addLegend(pal = factpal,
            title = "Cluster ID",
            values = ~ClusterID,
            opacity = 1.0) 
     
  } else {
    
    if (input$car_Variable == "GDP per Capita"){
    
    qpal1 <- colorQuantile("Greens",
                      domain = data_leaf$GDP_cap,
                      n = 5)

     leaf_Maps = leaflet(data = data_leaf, 
        options = leafletOptions(minZoom = 2, maxZoom = 5)) %>% 
  setView(lng = 15, lat = 55, zoom = 3) %>% 
  addProviderTiles(providers$CartoDB.Positron,
                   options = providerTileOptions(opacity = 0.5)) %>% 
  addPolygons(
    # color = "green", 
    #           opacity = .5,
    #           stroke = TRUE,
              weight = 1,
              fillOpacity = .7,
              # color = ~color(),
              fillColor = ~colorQuantile("Greens",  GDP_cap)(GDP_cap),
              label = ~paste0("Country: ", 
                              Country , 
                              " - ",
                              "GDP per Capita: ", 
                              prettyNum(round(GDP_cap,0), big.mark = ".")),
              highlight = highlightOptions(weight = 2,
                                           color = "white",
                                           bringToFront = TRUE)) %>% 
  addLegend(pal = qpal1,
            title = "Quantiles",
            values = ~GDP_cap,
            opacity = 1.0,
            labFormat = labelFormat(transform = function(x) round(100*x)))

    
    
    } else {
    
qpal2 <- colorQuantile("Reds",
                      domain = data_leaf$Registration,
                      n = 5)

     leaf_Maps = leaflet(data = data_leaf, 
          #                %>% 
          # filter(Year == input$car_Year),
        options = leafletOptions(minZoom = 2, maxZoom = 5)) %>% 
  setView(lng = 15, lat = 55, zoom = 3) %>% 
  addProviderTiles(providers$CartoDB.Positron,
                   options = providerTileOptions(opacity = 0.5)) %>% 
  addPolygons(
    # color = "red", 
    #           opacity = .5,
    #           stroke = TRUE,
              weight = 1,
              fillOpacity = .7,
              # color = ~color(),
              fillColor = ~colorQuantile("Reds",  Registration)(Registration),
              label = ~paste0("Country: ", 
                              Country , 
                              " - ",
                              "Registrations (promilles): ", 
                              prettyNum(round(Registration,1), accuracy = 1)),
              highlight = highlightOptions(weight = 2,
                                           color = "white",
                                           bringToFront = TRUE)) %>% 
  addLegend(pal = qpal2,
            title = "Quantiles",
            values = ~Registration,
            opacity = 1.0,
            labFormat = labelFormat(transform = function(x) round(100*x)))      
      
      
  }}

    leaf_Maps

  })


# Related data for DT - Tab 1
react_car_MapDT_Clust <- reactive({
    
    data_MapDT_Clust <- PCA_CAR_NRG_imp_glong %>% 
      st_drop_geometry() %>% 
      filter(Year == input$car_Year) %>% 
    select(Country, Country_Name, ClusterID)  %>% 
      distinct() %>% 
      arrange(ClusterID, Country) 
    
    data_MapDT_Clust

})


# Related data for DT - Tab 2
react_car_MapDT_GDP <- reactive({

    data_MapDT_GDP <- PCA_CAR_NRG_imp_glong %>% 
      st_drop_geometry() %>% 
      filter(Year == input$car_Year) %>% 
    select(Country, GDP_cap) %>% 
      distinct() %>% 
      arrange(-GDP_cap) 
    
    data_MapDT_GDP

})

# Related data for DT - Tab 3
react_car_MapDT_Nrg <- reactive({

    data_MapDT_Nrg <- PCA_CAR_NRG_imp_glong %>% 
      st_drop_geometry() %>% 
      filter(Year == input$car_Year) %>% 
    select(Country, Energy, Registration) %>% 
      filter(Energy == input$car_Variable) %>% arrange(-Registration)
    
    data_MapDT_Nrg

})

```



Row {data-height=100}
-----------------------------------------------------------------------

```{r inputs_reg_map}

selectInput("car_Year",
            "Select a year:",
            choices = c(2013, 2017))

selectInput("car_Variable",
            "Select an indicator:",
            choices = c("Cluster ID", 
                        "GDP per Capita", 
                        levels(PCA_CAR_NRG_imp_glong$Energy)))

```


Row {.sidebar data-width=600}
-----------------------------------------------------------------------


```{r reg_map}

renderLeaflet({
  
  react_car_leaf()
  
}) 

hr()

h5(strong("About European Thematic Maps ...")) #,
                                   p(h5("These maps aim at synthesizing the main findings from the previous multivariate analysis:"))

                                   p(h5("1. The", strong("3 map types"), "group European countries into quantiles based on their per capita GDP or engine-type-registration numbers.")) #,
                                   p(h5("2. The associated", strong("3 tables"),"on the right lay out detailed informations about the visualisations with the latest energy-type-registration amounts.")) #))

```


Row {data-width=400 .tabset}
-----------------------------------------------------------------------

### Cluster IDs

```{r reg_cluster_DT}
DT::renderDataTable({

datatable(react_car_MapDT_Clust(),
          rownames=FALSE,
          extensions = c("FixedColumns"),
          options = list(scrollX = TRUE, 
                         fixedColumns = list(leftColumns = 2),
                         pageLength=10,
                         # columnDefs = list(list(className = 'dt-center', targets = 1:3)), 
                         language = list(sSearch = "Filter:")))  

})
```


### GDP Per Capita

```{r reg_GDP_DT}

DT::renderDataTable({

datatable(react_car_MapDT_GDP(),
          rownames=FALSE,
          extensions = c("FixedColumns"),
          options = list(scrollX = TRUE, 
                         fixedColumns = list(leftColumns = 2),
                         pageLength=10,
                         # columnDefs = list(list(className = 'dt-center', targets = 1:2)), 
                         language = list(sSearch = "Filter:")))  %>% 
formatRound("GDP_cap", digits = 0)
  
})
```


### Top Car Energy Forms

```{r reg_energy_DT}

DT::renderDataTable({

datatable(react_car_MapDT_Nrg(),
          rownames=FALSE,
          extensions = c("FixedColumns"),
          options = list(scrollX = TRUE, 
                         fixedColumns = list(leftColumns = 2),
                         pageLength=10,
                         # columnDefs = list(list(className = 'dt-center')), # , targets = 1:5
                         language = list(sSearch = "Filter:")))  %>% 
formatRound("Registration", digits = 1)
  
})
```



Growth Maps {data-orientation=columns}
===============================================================================


```{r input_gr_map}

selectInput("car_gr_Variable",
            "Select an indicator:",
            choices = c("Cluster ID", 
                        "GDP per Capita", 
                        levels(PCA_carnrg_1517_gr_imp_glong$Energy)))


```



```{r react_gr_map}

react_hcpc_gr <- reactive({

    data_hcpc <- res.hcpc

    data_hcpc
    
  })


### Plotting Map data - From WIDE DATA!

react_car_leaf_gr <- reactive({
  
  data_leaf_gr = PCA_carnrg_1517_gr_imp_glong 
  
  if (input$car_gr_Variable == "Cluster ID"){

    
     factpal <- colorFactor(palette = "Dark2", 
                       unique(data_leaf_gr$ClusterID),
                       n = 4)
      

     leaf_gr_Maps = leaflet(data = data_leaf_gr, 
                            options = leafletOptions(minZoom = 2, maxZoom = 5)) %>% 
  setView(lng = 15, lat = 55, zoom = 3) %>% 
  addProviderTiles(providers$CartoDB.Positron,
                   options = providerTileOptions(opacity = 0.5)) %>% 
  addPolygons(stroke = FALSE,
    # color = "grey", 
    #           opacity = .5,
    #           stroke = TRUE, 
              smoothFactor = 0.2, 
              fillOpacity = .7,
              color = ~factpal(data_leaf_gr$ClusterID),
              label = ~paste0("Country: ", 
                              Country , 
                              " - ",
                              "Cluster ID: ", 
                              ClusterID),
              highlight = highlightOptions(weight = 2,
                                           color = "white",
                                           bringToFront = TRUE)) %>% 
  addLegend(pal = factpal,
            title = "Cluster ID",
            values = ~ClusterID,
            opacity = 1.0) 
     
  } else {
    
    if (input$car_gr_Variable == "GDP per Capita"){
    
    qpal1 <- colorQuantile("Greens",
                      domain = unique(data_leaf_gr$GDP_cap), 
                      n = 5)

     leaf_gr_Maps = leaflet(data = data_leaf_gr, 
                            options = leafletOptions(minZoom = 2, maxZoom = 5)) %>% 
  setView(lng = 15, lat = 55, zoom = 3) %>% 
  addProviderTiles(providers$CartoDB.Positron,
                   options = providerTileOptions(opacity = 0.5)) %>% 
  addPolygons(
    # color = "green", 
    #           opacity = .5,
    #           stroke = TRUE,
              weight = 1,
              fillOpacity = .7,
              # color = ~color(),
              fillColor = ~colorQuantile("Greens",  GDP_cap)(GDP_cap),
              label = ~paste0("Country: ", 
                              Country , 
                              " - ",
                              "GDP per Capita: ", 
                              prettyNum(round(GDP_cap,0), big.mark = ".")),
              highlight = highlightOptions(weight = 2,
                                           color = "white",
                                           bringToFront = TRUE)) %>% 
  addLegend(pal = qpal1,
            title = "Quantiles",
            values = ~GDP_cap,
            opacity = 1.0,
            labFormat = labelFormat(transform = function(x) round(100*x)))

    
    
    } else {
    
qpal2 <- colorQuantile("Reds",
                      domain = data_leaf_gr %>% 
                        filter(Energy == input$car_gr_Variable) %>% 
                        pull(GrowthRates),
                      n = 5)

     leaf_gr_Maps = leaflet(data_leaf_gr %>% 
                              filter(Energy == input$car_gr_Variable), 
                            options = leafletOptions(minZoom = 2, maxZoom = 5)) %>% 
  setView(lng = 15, lat = 55, zoom = 3) %>% 
  addProviderTiles(providers$CartoDB.Positron,
                   options = providerTileOptions(opacity = 0.5)) %>% 
  addPolygons(
    # color = "red", 
    #           opacity = .5,
    #           stroke = TRUE,
              weight = 1,
              fillOpacity = .7,
              # color = ~color(),
              fillColor = ~colorQuantile("Reds",  GrowthRates)(GrowthRates),
              label = ~paste0("Country: ", 
                              Country , 
                              " - ",
                              "Growth Rates (%): ", 
                              prettyNum(round(GrowthRates,1), accuracy = 1)),
              highlight = highlightOptions(weight = 2,
                                           color = "white",
                                           bringToFront = TRUE)) %>% 
  addLegend(pal = qpal2,
            title = "Quantiles",
            values = ~GrowthRates,
            opacity = 1.0,
            labFormat = labelFormat(transform = function(x) round(100*x)))      
      
      
  }}

    leaf_gr_Maps

  })



### DT cluster - Wide DATA

react_car_gr_MapDT_Clust <- reactive({

    data_gr_MapDT_Clust <- PCA_carnrg_1517_gr_gimp %>% 
      st_drop_geometry() %>% 
    select(Country, Country_Name, ClusterID)  %>% 
      arrange(ClusterID, Country) 
    
    data_gr_MapDT_Clust

})

### DT_GDP
react_car_gr_MapDT_GDP <- reactive({

    data_gr_MapDT_GDP <- PCA_carnrg_1517_gr_gimp %>% 
      st_drop_geometry() %>% 
    select(Country, GDP_cap = gdp_cap) %>% 
      arrange(-GDP_cap) 
    
    data_gr_MapDT_GDP

})

### Col_gr_Variables
react_car_gr_MapDT_Nrg <- reactive({

    data_gr_MapDT_Nrg <- PCA_carnrg_1517_gr_imp_glong %>% 
      filter(Energy == input$car_gr_Variable) %>% 
    select(Country, Energy, GrowthRates) %>% # 
      arrange(-GrowthRates)
    
    data_gr_MapDT_Nrg

})
  


```



Column {data-width=600, .tabset}
-----------------------------------------------------------------------


### Europe Map


```{r gr_geo_map}

renderLeaflet({
  
  react_car_leaf_gr()
  
}) 

hr()

h5(strong("About Cluster Analysis ...")) #,
                                   p(h5("These plots aim at clustering countries into groups showing overall similar characteristics in terms of car-engine types:"))

                                   p(h5("1. The", strong("5 clusters"), "were obtained using dimensionality reduction (PCA) and hierarchical clustering techniques.")) #,
                                   p(h5("2. The first", strong("4 dimensions"),"represents about 90 pct. of the variability in the dataset.")) #))
                       
```



### Cluster Map

```{r gr_cluster_map}

renderPlot({

fviz_cluster(react_hcpc_gr(),
             axes = 1:2,
             repel = T,
             ggtheme = theme_bw() +
  theme(text = element_text(family = "serif", size = 14),
        title = element_text(color = "#990000")))

  })

hr()

h5(strong("About Cluster Analysis ...")) #,
                                   p(h5("These plots aim at clustering countries into groups showing overall similar characteristics in terms of car-engine types:"))

                                   p(h5("1. The", strong("5 clusters"), "were obtained using dimensionality reduction (PCA) and hierarchical clustering techniques.")) #,
                                   p(h5("2. The first", strong("4 dimensions"),"represents about 90 pct. of the variability in the dataset.")) #))
                       
```



Column {data-width=400 .tabset}
-----------------------------------------------------------------------

### Cluster IDs


```{r gr_clust_DT}

### DT cluster

DT::renderDataTable({

datatable(react_car_gr_MapDT_Clust(),
          rownames=FALSE,
          extensions = c("FixedColumns"),
          options = list(scrollX = TRUE, 
                         fixedColumns = list(leftColumns = 2),
                         pageLength=10,
                         # columnDefs = list(list(className = 'dt-center', targets = 1:3)), 
                         language = list(sSearch = "Filter:")))  

})


```



### GDP Per Capita

```{r gr_GDP_DT}

### DT_GDP

DT::renderDataTable({

datatable(react_car_gr_MapDT_GDP(),
          rownames=FALSE,
          extensions = c("FixedColumns"),
          options = list(scrollX = TRUE, 
                         fixedColumns = list(leftColumns = 2),
                         pageLength=10,
                         # columnDefs = list(list(className = 'dt-center', targets = 1:2)),
                         language = list(sSearch = "Filter:")))  %>% 
formatRound("GDP_cap", digits = 0)
  
})



```



### Top Energy-Form Growth Rates



```{r gr_energy_DT}

renderPlotly({

gg_gr_Nrg = react_car_gr_MapDT_Nrg() %>% 

  ggplot(aes(fct_reorder(Country, GrowthRates), GrowthRates)) +
  geom_col(fill = "#d7301f") +
  scale_x_discrete("") +
  scale_y_continuous("Growth Rates (percent)") +
  coord_flip() + 
  theme_minimal()

ggplotly(gg_gr_Nrg, tooltip = c("Country"))

})

```





Cluster Analysis (2013)
===============================================================================

Row {data-height=100}
-----------------------------------------------------------------------

```{r react_cluster_13, include=FALSE}

react_hcpc_13 <- reactive({

    data_hcpc_13 <- res13.hcpc

    data_hcpc_13
    
  })


react_axes_fviz_13 = reactive({

  axes = c()
  
    if(input$car_13_dims == "Dimensions 1 and 2"){
      
     axes = 1:2 } else {
     axes = 3:4
      
      
    }

    axes
    
  })


### Dim 13 - Cadre 1 -Tab 1
react_top_13_dim13_c1 = reactive({
  
  if(input$car_13_dims == "Dimensions 1 and 2"){
   
gg_13_dim13_c1 = data_res13.pca %>% 
  select(Country, ALT) %>% 
  arrange(desc(ALT)) %>% 
  rename(Alternative = ALT) %>% 
  top_n(5) %>% 
  ggplot(aes(fct_reorder(Country, Alternative), Alternative)) +
  geom_col(fill = "#99000d") +
  scale_x_discrete("") +
  scale_y_continuous("Alternative Engine Registrations (per thousand)") +
  coord_flip() + theme_minimal()   
    
 } else {
   
   gg_13_dim13_c1 = data_res13.pca %>% 
  select(Country, DIE) %>% 
  arrange(desc(DIE)) %>% 
  rename(Diesel = DIE) %>% 
  top_n(5) %>% 
  ggplot(aes(fct_reorder(Country, Diesel), Diesel)) +
  geom_col(fill = "#cb181d") +
  scale_x_discrete("") +
  scale_y_continuous("Diesel Registrations (per thousand)") +
  coord_flip() + theme_minimal()
  
    


  }
    
gg_13_dim13_c1   
    


})


### Dim 13 - Cadre 2 - Tab 1
react_top_13_dim13_c2 = reactive({
  
  if(input$car_13_dims == "Dimensions 1 and 2"){
    
    
gg_13_dim13_c2 = data_res13.pca %>% 
  select(Country, ELC) %>%
  arrange(desc(ELC)) %>%
  rename(Electric = ELC) %>%
  top_n(5) %>%
  ggplot(aes(fct_reorder(Country, Electric), Electric)) +
  geom_col(fill = "#fdd49e") +
  scale_x_discrete("") +
  scale_y_continuous("Electrical Engine Registrations (per thousand)") +
  coord_flip() + theme_minimal()  } else {
  
    
gg_13_dim13_c2 = data_res13.pca %>% 
  select(Country, DIE_X_HYB) %>% 
  arrange(desc(DIE_X_HYB)) %>% 
  rename(Diesel_NoHybrid = DIE_X_HYB) %>% 
  top_n(5) %>% 
  ggplot(aes(fct_reorder(Country, Diesel_NoHybrid), Diesel_NoHybrid)) +
  geom_col(fill = "#fdbb84") +
  scale_x_discrete("") +
  scale_y_continuous("Diesel excl. Hybrid Registrations (per thousand)") +
  coord_flip()  + theme_minimal()

  }
    
gg_13_dim13_c2   
    


})


### Dim 24 - Cadre 1 - Tab 2
react_top_13_dim24_c1 = reactive({
  
  if(input$car_13_dims == "Dimensions 1 and 2"){
    
    
gg_13_dim24_c1  = data_res13.pca %>% 
  select(Country, PET_X_HYB) %>%
  arrange(desc(PET_X_HYB)) %>%
  rename(Petrolium_NoHybrid = PET_X_HYB) %>%
  top_n(5) %>%
  ggplot(aes(fct_reorder(Country, Petrolium_NoHybrid), Petrolium_NoHybrid)) +
  geom_col(fill = "#fc8d59") +
  scale_x_discrete("") +
  scale_y_continuous("Petrolium excl. Hybrid Registrations (per thousand)") +
  coord_flip()  + theme_minimal() } else {
  
    
gg_13_dim24_c1 = data_res13.pca %>% 
  select(Country, OTH) %>% 
  arrange(desc(OTH)) %>% 
  rename(Other = OTH) %>% 
  top_n(5) %>% 
  ggplot(aes(fct_reorder(Country, Other), Other)) +
  geom_col(fill = "#ef6548") +
  scale_x_discrete("") +
  scale_y_continuous("Other Engine Registrations (per thousand)") +
  coord_flip()  + theme_minimal()

  }
    
gg_13_dim24_c1   
    


})


### Dim 24 - Cadre 2 - Tab 2
react_top_13_dim24_c2 = reactive({
  
  if(input$car_13_dims == "Dimensions 1 and 2"){
    
    
gg_13_dim24_c2  = data_res13.pca %>% 
  select(Country, PET) %>%
  arrange(desc(PET)) %>%
  rename(Petrolium = PET) %>%
  top_n(5) %>%
  ggplot(aes(fct_reorder(Country, Petrolium), Petrolium)) +
  geom_col(fill = "#d7301f") +
  scale_x_discrete("") +
  scale_y_continuous("Petrolium Engine Registrations (per thousand)") +
  coord_flip() + theme_minimal()  } else {
  
    
gg_13_dim24_c2 = data_res13.pca %>% 
  select(Country, GAS) %>% 
  arrange(GAS) %>% 
  rename(Gas = GAS) %>% 
  top_n(5) %>% 
  ggplot(aes(fct_reorder(Country, Gas), Gas)) +
  geom_col(fill = "#990000") +
  scale_x_discrete("") +
  scale_y_continuous("Gas Engine Registrations (per thousand)") +
  coord_flip()  + theme_minimal()

  }
    
gg_13_dim24_c2   
    


})



```



```{r input_clust_13}

selectInput("car_13_dims",
            "Select the dimensions of the cluster:",
            choices = c("Dimensions 1 and 2", "Dimensions 3 and 4"))

```



Row {.sidebar data-width=600}
-----------------------------------------------------------------------


```{r clust_13_map}

renderPlot({

fviz_cluster(react_hcpc_13(), 
             axes = react_axes_fviz_13(), 
             repel = T, 
             ggtheme = theme_bw() +
  theme(text = element_text(family = "serif", size = 14),
        title = element_text(color = "#990000")))
  
  })

hr()

h5(strong("About Cluster Analysis ...")) #,
                                   p(h5("These plots aim at clustering countries into groups showing overall similar characteristics in terms of car-engine types:"))

                                   p(h5("1. The", strong("5 clusters"), "were obtained using dimensionality reduction (PCA) and hierarchical clustering techniques.")) #,
                                   p(h5("2. The first", strong("4 dimensions"),"represents about 90 pct. of the variability in the dataset.")) #))
                       
```



Row {data-width=400 data-height=500 .tabset}
-----------------------------------------------------------------------

### Top `r reactive(ifelse(input$car_13_dims == "Dimensions 1 and 2", "Alternative Engine", "Diesel Engine"))` Registrations



```{r clust_13_col_dim13_11}

### Cadre 1 - Tab 1
renderPlotly({
  
ggplotly(react_top_13_dim13_c1(), tooltip = c("Country"))
  
})


```



### Top `r reactive(ifelse(input$car_13_dims == "Dimensions 1 and 2", "Electrical Engine", "Diesel excl. Hybrids"))` Registrations

```{r clust_13_col_dim13_12}

### Cadre 1 - Tab 2

renderPlotly({
  
ggplotly(react_top_13_dim13_c2(), tooltip = c("Country"))
  
})

```


Row {data-width=400 data-height=500 .tabset}
-----------------------------------------------------------------------

### Top `r reactive(ifelse(input$car_13_dims == "Dimensions 1 and 2", "Petrolium excl. Hybrids", "Other Engine"))` Registrations



```{r clust_13_col_dim24_21}

### Cadre 2 - Tab 1

renderPlotly({
  
ggplotly(react_top_13_dim24_c1(), tooltip = c("Country"))
  
})


```



### Top `r reactive(ifelse(input$car_13_dims == "Dimensions 1 and 2", "Petrolium Engine", "Gas Engine"))` Registrations

```{r clust_13_col_dim24_22}

### Cadre 2 - Tab 2

renderPlotly({
  
ggplotly(react_top_13_dim24_c2(), tooltip = c("Country"))
  
})

```




Cluster Analysis (2017)
===============================================================================

Row {data-height=100}
-----------------------------------------------------------------------

```{r react_clust_17, include=FALSE}

# res17.hcpc

react_hcpc_17 <- reactive({

    data_hcpc_17 <- res17.hcpc

    data_hcpc_17
  })


react_axes_fviz_17 = reactive({

  axes = c()
  
    if(input$car_17_dims == "Dimensions 1 and 2"){
      
     axes = 1:2 } else {
     axes = 3:4
      
      
    }

    axes
    
  })


### Dim 13 - Cadre 1 - Tab 1 - PCA relevant variables
react_top_17_dim13_c1 = reactive({
  
  if(input$car_17_dims == "Dimensions 1 and 2"){
    
    
gg_17_dim13_c1 = data_res17.pca %>% 
  select(Country, DIE) %>% 
  arrange(desc(DIE)) %>% 
  rename(Diesel = DIE) %>% 
  top_n(5) %>% 
  ggplot(aes(fct_reorder(Country, Diesel), Diesel)) +
  geom_col(fill = "#225ea8") +
  scale_x_discrete("") +
  scale_y_continuous("Diesel Registrations (per thousand)") +
  coord_flip() +
  theme_minimal() } else {
  
    
gg_17_dim13_c1 = data_res17.pca %>% 
  select(Country, OTH) %>% 
  arrange(desc(OTH)) %>% 
  rename(Other = OTH) %>% 
  top_n(5) %>% 
  ggplot(aes(fct_reorder(Country, Other), Other)) +
  geom_col(fill = "#0c2c84") +
  scale_x_discrete("") +
  scale_y_continuous("Other Engine Registrations (per thousand)") +
  coord_flip() + theme_minimal() 

  }
    
gg_17_dim13_c1   
    


})




### Dim 13 - Cadre 2 - Tab 1 - PCA relevant variables
react_top_17_dim13_c2 = reactive({
  
  if(input$car_17_dims == "Dimensions 1 and 2"){
    
    
gg_17_dim13_c2 = data_res17.pca %>% 
  select(Country, ELC) %>%
  arrange(desc(ELC)) %>%
  rename(Electric = ELC) %>%
  top_n(5) %>%
  ggplot(aes(fct_reorder(Country, Electric), Electric)) +
  geom_col(fill = "#c6dbef") +
  scale_x_discrete("") +
  scale_y_continuous("Electrical Engine Registrations (per thousand)") +
  coord_flip() + theme_minimal()  } else {
  
    
gg_17_dim13_c2 = data_res17.pca %>% 
  select(Country, PET_X_HYB) %>% 
  arrange(desc(PET_X_HYB)) %>% 
  rename(Petrolium_NoHybrid = PET_X_HYB) %>% 
  top_n(5) %>% 
  ggplot(aes(fct_reorder(Country, Petrolium_NoHybrid), Petrolium_NoHybrid)) +
  geom_col(fill = "#9ecae1") +
  scale_x_discrete("") +
  scale_y_continuous("Petrolium excl. Hybrid Registrations (per thousand)") +
  coord_flip()  + theme_minimal()

  }
    
gg_17_dim13_c2   
    


})



### Dim 24 - Cadre 1 - Tab 2 - PCA relevant variables
react_top_17_dim24_c1 = reactive({
  
  if(input$car_17_dims == "Dimensions 1 and 2"){
    
    
gg_17_dim24_c1  = data_res17.pca %>% 
  select(Country, PET) %>%
  arrange(desc(PET)) %>%
  rename(Petrolium = PET) %>%
  top_n(5) %>%
  ggplot(aes(fct_reorder(Country, Petrolium), Petrolium)) +
  geom_col(fill = "#6baed6") +
  scale_x_discrete("") +
  scale_y_continuous("Petrolium Engine Registrations (per thousand)") +
  coord_flip() + theme_minimal()  } else {
  
    
gg_17_dim24_c1 = data_res17.pca %>% 
  select(Country, GAS) %>% 
  arrange(desc(GAS)) %>% 
  rename(Gas = GAS) %>% 
  top_n(5) %>% 
  ggplot(aes(fct_reorder(Country, Gas), Gas)) +
  geom_col(fill = "#4292c6") +
  scale_x_discrete("") +
  scale_y_continuous("Gas Engine Registrations (per thousand)") +
  coord_flip()  + theme_minimal()

  }
    
gg_17_dim24_c1   
    


})


### Dim 24 - Cadre 2 - Tab 2 - PCA relevant variables
react_top_17_dim24_c2 = reactive({
  
  if(input$car_17_dims == "Dimensions 1 and 2"){
    
    
gg_17_dim24_c2  = data_res17.pca %>% 
  select(Country, ALT) %>%
  arrange(desc(ALT)) %>%
  rename(Alternative = ALT) %>%
  top_n(5) %>%
  ggplot(aes(fct_reorder(Country, Alternative), Alternative)) +
  geom_col(fill = "#2171b5") +
  scale_x_discrete("") +
  scale_y_continuous("Alternative Engine Registrations (per thousand)") +
  coord_flip() + theme_minimal()  } else {
  
    
gg_17_dim24_c2 = data_res17.pca %>% 
  select(Country, GAS) %>% 
  arrange(GAS) %>% 
  rename(Gas = GAS) %>% 
  top_n(5) %>% 
  ggplot(aes(fct_reorder(Country, Gas), Gas)) +
  geom_col(fill = "#084594") +
  scale_x_discrete("") +
  scale_y_continuous("Gas Engine Registrations (per thousand)") +
  coord_flip()  + theme_minimal()

  }
    
gg_17_dim24_c2   
    


})



  
```




```{r input_clust_17}
selectInput("car_17_dims",
            "Select the dimensions of the cluster:",
            choices = c("Dimensions 1 and 2", "Dimensions 3 and 4"))

```



Row {.sidebar data-width=600}
-----------------------------------------------------------------------


```{r clust_17_map}

renderPlot({
 
fviz_cluster(react_hcpc_17(), 
             axes = react_axes_fviz_17(), 
             repel = T, 
             ggtheme = theme_bw() +
  theme(text = element_text(family = "serif", size = 14),
        title = element_text(color = "#990000"))) 
  
  })

hr()

h5(strong("About Cluster Analysis ...")) #,
                                   p(h5("These plots aim at clustering countries into groups showing overall similar characteristics in terms of car-engine types:"))

                                   p(h5("1. The", strong("5 clusters"), "were obtained using dimensionality reduction (PCA) and hierarchical clustering techniques.")) #,
                                   p(h5("2. The first", strong("4 dimensions"),"represents about 89 pct. of the variability in the dataset.")) #))
                       
```




Row {data-width=400 data-height=500 .tabset}
-----------------------------------------------------------------------


### Top `r reactive(ifelse(input$car_17_dims == "Dimensions 1 and 2", "Diesel Engine", "Other Engine"))` Registrations



```{r clust_17_col_dim13_11}

### Cadre 1 - Tab 1 
renderPlotly({
  
ggplotly(react_top_17_dim13_c1(), tooltip = c("Country"))
  
})


```



### Top `r reactive(ifelse(input$car_17_dims == "Dimensions 1 and 2", "Electrical Engine", "Petrolium excl. Hybrids"))` Registrations

```{r clust_17_col_dim13_12}
### Cadre 1 - Tab 2
renderPlotly({
  
ggplotly(react_top_17_dim13_c2(), tooltip = c("Country"))
  
})

```


Row {data-width=400 data-height=500 .tabset}
-----------------------------------------------------------------------


### Top `r reactive(ifelse(input$car_17_dims == "Dimensions 1 and 2", "Petrolium Engine", "Gas Engine"))` Registrations

```{r clust_17_col_dim24_21}
### Cadre 2 - Tab 1
renderPlotly({
  
ggplotly(react_top_17_dim24_c1(), tooltip = c("Country"))
  
})

```

### Top `r reactive(ifelse(input$car_17_dims == "Dimensions 1 and 2", "Alternative Engine", "Gas Engine"))` Registrations

```{r clust_17_col_dim24_22}
### Cadre 2 - Tab 2
renderPlotly({
  
ggplotly(react_top_17_dim24_c2(), tooltip = c("Country"))
  
})

```



Aggregated Time Series Data
===============================================================================

```{r reactive_TS, include = FALSE}

### Time Series of Car Energy
react_TS_energy = reactive({
  
  if(input$car_TS_energy == "Traditional Fuel"){
    
### Top traditional Energy engines
gg__TS_energy = ggplot(carb_year_long %>% 
                  filter(Registrations > 1000000), 
                aes(Year, Registrations, fill = Energy)) + 
           geom_area(alpha = 0.5) + 
  scale_x_continuous("") +
  scale_y_continuous("European Registrations",
                     labels = scales::comma_format(big.mark = ".")) +
  scale_fill_discrete("") +
  ggtitle("Number of registrations of fuel-engine-driven cars") +
  theme(legend.position = "top") +
  theme_minimal() +
  theme(text = element_text(family = "serif", size = 14),
        title = element_text(color = "#990000"))  } else { 
             
             if(input$car_TS_energy == "Electrically Driven") {

### Top Electrical and Hybrid Energy Engines
gg__TS_energy = ggplot(carb_year_long %>% 
                  filter(Energy %in% c("Electrical",
                                       "Hybrid electric-petrol",
                                       "Plug-in hybrid petrol-electric",
                                       "Hybrid diesel-electric",
                                       "Plug-in hybrid diesel-electric")),
                aes(Year, Registrations, fill = Energy)) + 
           geom_area(alpha = .5) + 
  scale_x_continuous("") +
  scale_y_continuous("European Registrations",
                     labels = scales::comma_format(big.mark = ".")) +
  scale_fill_discrete("") +
  ggtitle("Number of registrations of electrical-engine-driven cars") +
  theme(legend.position = "top") +
  theme_minimal() +
  theme(text = element_text(family = "serif", size = 14),
        title = element_text(color = "#990000"))  } else {
             

### Top Alternative Energy Engines
gg__TS_energy = ggplot(carb_year_long %>% 
                  filter(Energy %in% c("Alternative",
                                       "Gas",
                                       "Liquefied petroleum gases",
                                       "Other")),
                aes(Year, Registrations, fill = Energy)) + 
           geom_area(alpha = .5) +
  scale_x_continuous("") +
  scale_y_continuous("European Registrations",
                     labels = scales::comma_format(big.mark = ".")) +
  scale_fill_discrete("") +
  ggtitle("Registrations of alternative-energy-driven cars") +
  theme(legend.position = "top") +
  theme_minimal() +
  theme(text = element_text(family = "serif", size = 14),
        title = element_text(color = "#990000"))

             
           }}
 
  gg__TS_energy 
  
})



### Time Series of Car Energy
react_DT_energy = reactive({
  
  if(input$car_TS_energy == "Traditional Fuel"){
    
### Top traditional Energy engines
data__DT_energy = carb_year_long %>% 
                  filter(Energy %in% c("Diesel", 
                                       "Petrolium",
                                       "Petrol excl. hybrids", 
                                       "Diesel excl. hybrids"))
                         
                         } else { 
             
             if(input$car_TS_energy == "Electrically Driven") {

### Top Electrical and Hybrid Energy Engines
data__DT_energy = carb_year_long %>% 
                  filter(Energy %in% c("Electrical",
                                       "Hybrid electric-petrol",
                                       "Plug-in hybrid petrol-electric",
                                       "Hybrid diesel-electric",
                                       "Plug-in hybrid diesel-electric"))

} else {
             
### Top Alternative Energy Engines
data__DT_energy = carb_year_long %>% 
                  filter(Energy %in% c("Alternative",
                                       "Gas",
                                       "Liquefied petroleum gases",
                                       "Other"))
           }}
 
data__DT_energy 
  
})

```



Row {data-height=100}
-----------------------------------------------------------------------

```{r input_TS}
selectInput("car_TS_energy",
            "Select a car's energy form:",
            choices = c("Traditional Fuel", "Electrically Driven", "Alternative"))
```



Row {.sidebar data-width=600}
-----------------------------------------------------------------------


```{r TS_plots}

renderPlotly({
  
  ggplotly(react_TS_energy())
  
})  

hr()

h5(strong("About the Time Series Data ...")) #,
                                   p(h5("These time series aim at showing the evolution of engine-type-registration numbers at the European aggregate level for 3 car-engine categories:"))

                                   p(h5("1. The more", strong("traditional-fuel-driven-engines"), "based on petrolium and diesel.")) #,
                                   p(h5("2. The trendier", strong("electric-driven-engines"),"(grouping pure electrical or petrolium/diesel-hybrid-based engines.")) #))
                                   p(h5("3. ", strong("Alternative-energy-form-engines"), "listing gas and LPG fuels among others.")) #

```



Row {data-width=400}
-----------------------------------------------------------------------

### Aggregated Time Series Data

```{r TS_DT}
DT::renderDataTable({

datatable(react_DT_energy() %>%  
            arrange(-Year, -Registrations),
          rownames=FALSE,
          extensions = c("FixedColumns"),
          options = list(scrollX = TRUE, 
                         fixedColumns = list(leftColumns = 2),
                         pageLength=10,
                         # columnDefs = list(list(className = 'dt-center')), # , targets = 1:5
                         language = list(sSearch = "Filter:")))  %>% 
formatRound("Registrations", 
            mark = ".", 
            digits = 0)
})
```


